Cooperative Kernels: GPU Multitasking for Blocking Algorithms

### 2017-02-27 write-ups/FSE/paper.tex
Fixed some typos.

Some recent GPUs, including Nvidia's Pascal architecture, provide
hardware support for instruction-level preemption.  Few details of how
this works are available, but from reading Nvidia documentation and
online material~\cite{PascalWhitepaper,anandtech}, our understanding
is that preemption of entire kernels, but not of individual workgroups
is supported.  Intel GPUs do not provide this feature, and out OpenCL
2.0 prototype of cooperative kernels cannot run on Nvidia GPUs, making
a direct comparison impossible.  We present here a theoretical
analysis of the overheads associated with sharing the GPU between
graphics and compute tasks via kernel-level preemption.

Given a graphics workload that is required to be scheduled with period
$P$ and duration $D$, and that a compute kernel requires time $C$ to
execute without interruption.  If we assume the cost of preemption is
negligible (e.g.\ Nvidia have reported preemption times of 0.1 ms for
Pascal~\cite{anandtech}), then the overhead associated with switching
between compute and graphics every $P$ time steps is $P/(P-D)$.

>>>>

Some recent GPUs, including Nvidia's Pascal architecture, provide
hardware support for instruction-level preemption.  Few details of how
this works are available, but from reading Nvidia documentation and
online material~\cite{PascalWhitepaper,anandtech}, our understanding
is that preemption of entire kernels, but not of individual workgroups
is supported.  Intel GPUs do not provide this feature, and our OpenCL
2.0 prototype of cooperative kernels cannot run on Nvidia GPUs, making
a direct comparison impossible.  We present here a theoretical
analysis of the overheads associated with sharing the GPU between
graphics and compute tasks via kernel-level preemption.

Suppose a graphics workload is required to be scheduled with period
$P$ and duration $D$, and that a compute kernel requires time $C$ to
execute without interruption.  If we assume the cost of preemption is
negligible (e.g.\ Nvidia have reported preemption times of 0.1 ms for
Pascal~\cite{anandtech}), then the overhead associated with switching
between compute and graphics every $P$ time steps is $P/(P-D)$.
